---
title: "UNICEF REPORT ON MALNUTRITION AROUND THE WORLD"
author: "Akshay Sawant"
date: 30th April 2023
format: html
execute: 
  echo: true
  warning: false
  message: false
---

# **UNICEF's "Wasted, Overweight or Stunted" Indicator Report**

## **Introduction**

This report provides an overview of **UNICEF's "Wasted, Overweight or Stunted"** indicator, which measures the prevalence of malnutrition among children under the age of five. This report includes four visualizations that showcase the data related to this indicator, along with an analysis of the data around the world.

The "Wasted, Overweight or Stunted" indicator provides a comprehensive measure of malnutrition that takes into account both acute and chronic forms of malnutrition, as well as overnutrition. It is often used as an indicator of overall child health and well-being, as malnutrition can have serious long-term health effects on children, including impaired cognitive and physical development, increased risk of disease, and lower life expectancy.

To better understand the data related to this indicator, several visualizations have been plotted to showcase the prevalence of malnutrition around the world.

## **Top 10 Countries with the Highest Levels of Malnutrition**

### **Overview**

The first visualization shows the top 10 countries with the highest levels of malnutrition. The data reveals that the majority of these countries are located in Sub-Saharan Africa and South Asia. These regions also have the highest rates of poverty and the most limited access to basic healthcare and nutrition services.

### **Results**

- India: 21.2%
- Nigeria: 19.3%
- Pakistan: 17.0%
- Indonesia: 11.4%
- Ethiopia: 10.9%
- Bangladesh: 9.7%
- Democratic Republic of the Congo: 8.0%
- United Republic of Tanzania: 7.8%
- Kenya: 7.3%
- Afghanistan: 6.9%

### **Visualization**

```{r}
# Load the required libraries
library(tidyverse)
library(sf)
library(rnaturalearth)
library(lwgeom)
library(dplyr)

# Import the unicef_indicator_2.csv file
data <- read_csv("unicef_indicator_2.csv")

# Clean and transform the data
clean_data <- data %>%
  drop_na() %>%
  filter(!is.na(obs_value) & obs_value >= 0)

# Filter for the top 20 countries with the highest obs_value
top_20 <- clean_data %>%
  group_by(country) %>%
  summarise(total_obs_value = sum(obs_value)) %>%
  top_n(20, total_obs_value)

# Load World Map dataset and make the geometry valid
world_map <- rnaturalearth::ne_countries(scale = "medium", returnclass = "sf") %>%
  st_make_valid()

# Create a lookup table to map country names to ISO A3 codes and join with top_20
top_20 <- top_20 %>%
  left_join(world_map %>% select(iso_a3, name_long) %>% distinct(), by = c("country" = "name_long"))

# Merge world_map and top_20 data frames
merged_data <- left_join(world_map, top_20, by = "iso_a3")

# Plot 20 countries with the highest obs_value
world_map_chart <- ggplot() +
  geom_sf(data = merged_data, aes(fill = total_obs_value), color = "white") +
  scale_fill_continuous(low = "blue", high = "red", na.value = "lightgreen", name = "Obs Value") +
  labs(title = "Top 20 Countries with the Highest Level of Malnutrition (Wasted, Overweight or Stunted)") +
  theme_minimal()

#View the Map 
world_map_chart

```

## **Relationship on POPVS Life Countries with the Highest Levels of Malnutrition**

### **Overview**

The first visualization shows the top 10 countries with the highest levels of malnutrition. The data reveals that the majority of these countries are located in Sub-Saharan Africa and South Asia. These regions also have the highest rates of poverty and the most limited access to basic healthcare and nutrition services.

### **Results**

- India: 21.2%
- Nigeria: 19.3%
- Pakistan: 17.0%
- Indonesia: 11.4%
- Ethiopia: 10.9%
- Bangladesh: 9.7%
- Democratic Republic of the Congo: 8.0%
- United Republic of Tanzania: 7.8%
- Kenya: 7.3%
- Afghanistan: 6.9%

### **Visualization**
```{r}
library(tidyverse)
library(sf)
library(rnaturalearth)
library(lwgeom)
library(dplyr)

# Load the clean data and add a row number column

clean_data$id <- 1:nrow(clean_data)

# Join the two datasets on the row number column
data_combined <- left_join(data_selected, clean_data, by = "country",relationship = "many-to-many")

# Create the scatter plot with linear regression line
ggplot(data_combined, aes(x = Life.expectancy.at.birth..total..years., y = Population..total, color = obs_value )) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ x, se = FALSE, color = "green") +
  ggtitle("Scatter Plot of Population vs Life Expectancy by Observed Value for Country") +
  xlab("Life Expectancy at birth") +
  ylab("Population Total") +
  theme_bw()

```

The `echo: false` option disables the printing of code (only output is displayed).
